%Tim Kirker

 We found the following problems with regards to the Send message Use Case of the module.
 \subsubsection*{Notification A}
 The notification module for team A had the following violations
 \begin{enumerate}
 	\item Pre condition:
 	\begin{itemize}
 		\item Check that the user is registered
			
		A function is used to determine whether or not the user has been registered to recieve notifications.
 		
		\item sends user email
 	\end{itemize}
	\item Post conditions:
	\begin{itemize}
		\item Function returns a message based on success or failure
			
		A message is created

		\item An email is sent to the user 
		
		The message is sent in an email to the registered user
 	
	\end{itemize}
	

	\item Data structure requirement violations:
 	\begin{itemize}
 		\item It did not take into account callback functions thus the date structure requirements are violated.
 		
 	\end{itemize}
 \end{enumerate}
 \subsubsection*{Notification B}
 The notification module for team B had the following violations
 \begin{enumerate}
 	\item Pre condition violations:
 	\begin{itemize}
 		
			\item Checks that the user is registered 
			
			A function is used to determine whether or not the user has been registered to recieve notifications.
			
			\item Takes in a JSON string
				
			It takes a string in the format FROM, TO, SUBJECT, PLAIN, HTML
 		
 		 
 	\end{itemize}
	\item Post conditions:
	\begin{itemize}
			\item A user is sent an email
			
			A user is sent an email using a JSON string, the email contains the recipients and the message.
 	
	\end{itemize}
	\item Data structure requirement violations:
 	\begin{itemize}
 		\item 	Makes use of callback functions thus nothing is being violated.
		\item	The email function itself is well structured and easy to follow.
 	\end{itemize}
 \end{enumerate}
 \subsubsection*{Remarks}
 Notification A did not fully do what was required in the functional requirements. However Notifications B seemed to have managed to cover all aspects of the functional requirements