% Johann Marx
% See template
The notification module had the following problems regarding performance of the notification system both A and B. 
\subsubsection*{Notification A}
\begin{itemize}
    \item No test file.
    To start off with, Notification A had no test file to actually test the performance with.
    \item Hardcoded
    Notification A has 306 lines of coding more than Notification B. It can also be noted that they had a lot of commented out work in their file, but it can be seen that it actually belongs there(so we are assuming they hid it for demo purposes).
    They did a lot of hardcoding, where as Notification B found a way of streamlining the process.
\end{itemize}
\subsubsection*{Notification B}
\begin{itemize}
    \item Buggy Test file
    Even though they had a test file for the coding, which was configured with nodeUnit to do unit tests etc.,
    The file did not finish the test.  It started testing, had no assertions, connected to the server, but then just stopped. This is mainly because of the .listened function which never ends automatically.
    \item Large file
    Compared to Notification A, Notification B has a 6.67x larger package file(20kb against 3kb).  Although this is still quite small overall,  it just shows that it could still have been programmed more compactly.(It has to be noted though that they do have unit tests, unlike Notification B).
\end{itemize}
\subsubsection*{Remarks}
The overall impression of both teams is that they did not meet the requirements that were needed. Although the performance was not the worst issue they had,  there is still a lot of room for improvement on both teams' work before a fully deployable product can come out of it.
